SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-09-17 scipy-1.0/paper.tex
Shorten

The development cost of SciPy is estimated in excess of 10M dollars by
Open Hub\cite{SciPyValue}.  Yet, the project is largely unfunded, having been
developed predominantly by graduate students, faculty, and members of industry
in their free time. Small amounts of funding have been applied with success:
some meetings were sponsored by universities and industry, Google's Summer of Code
program supported infrastructure and algorithmic work, and teaching grant funds were
used early on to develop documentation.  However, these small amounts of
sporadic funding are not commensurate with the enormous stack of important scientific
software, like those that are used to plan national space missions, that rely
on SciPy.
With traditional grant mechanisms, it is easier to buy software licenses than to support the diverse development effort needed to develop open source software—a challenge that we hope to see national funding agencies address.
The scientific Python stack is also playing an increasingly important role in industry, and while there are some encouraging signals such as TideFlow, that sector still spends comparatively little on community-developed software.
For open source projects to remain a healthy underpinning of international scientific and industrial endeavors, it needs more diverse spending to support planning, development, management, and infrastructure.

>>>>

The development cost of SciPy is estimated in excess of 10M dollars by
Open Hub\cite{SciPyValue}.  Yet, the project is largely unfunded, having been
developed predominantly by graduate students, faculty, and members of industry
in their free time. Small amounts of funding have been applied with success:
some meetings were sponsored by universities and industry, Google's Summer of Code
program supported infrastructure and algorithmic work, and teaching grant funds were
used early on to develop documentation.  However, funding from national agencies,
foundations, and industry has not been commensurate with the enormous stack of important
software that rely on SciPy.
More diverse spending to support planning, development, management, and infrastructure would
help SciPy remain a healthy underpinning of international scientific
and industrial endeavors.
